---
title: "Ecology data quick run through"
author: "Matt"
date: "12 8 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(packagefinder)
library(datasets.load)

```

### What types of data are there in ecology?

My quick thoughts and some example code on how we can get a representive (ish) sample of data from "ecological" focused R packages and to get an understanding of what types of data there are.

### Step 1 - get a list of ecology packages

```{r step 1}
packagefinder::findPackage(keywords = "ecology",display = "console",limit.results = 1000)

```

**Current challenges are:** 

* we need a better set of search terms as this really only gives a small subset of ecology focused packages (maybe someone somewhere has a list - maybe I can ask on Twitter)

* how do I get a list of packages from this? I submitted an issue at the package github page in the meantime it will have to be our old friend excel


### Step 2 - install all these packages 

```{r step 2}
pkgs<-c("AHMbook","algaeClassify","allelematch","analogue","aPCoA","BayesComm","bcpa","betaper","BIEN","BiodiversityR","blmeco","boral","cepreader","CNull","CommEcol","CoordinateCleaner","DAISIE","dave","DSAIDE","EcoSimR",#"ecospace",
        "ecospat","EMbC","ENMTools","enveomics.R","eRTG3D","expp","FD","FLightR","foieGras","forams","fso","genotypeR","gfcanalysis","hydrostats","inpdfr","labdsv","lconnect","letsR","loop","m2b","MCMC.OTU","mefa","meteR","move","mvabund","nicheROVER","nimbleEcology","NitrogenUptake2016","NLMR","nlraa","nna","nodiv","nsRFA","NST","OCNet","paleoMAS","petitr","pgirmess","philentropy","phyloregion","picante","polyfreqs","pop","primer","QFASA","raceland","RADanalysis","RAM","rangeMapper","Rbeast","Rdistance","RevEcoR","rfishbase","RRPP","SADISA","sampSurf","seas","Select","sharx","SiMRiv","SitesInterest","soundecology","SP2000","SSP","StAMPP","stockR","swapClass","TipDatingBeast","TITAN2","treeclim","TreeSimGM","tsvr","vegan","VGAM","VGAMdata","virtualNicheR","virtualspecies","wsyn","zoon")
#ecospace not available

#install all packages
list.of.packages <- pkgs
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

```


### Step 3 - explore the datasets for each package

```{r step 3}
datasets_list<-datasets.load::getDatasetInfo(pkgs)
datasets_tibble<-as_tibble(datasets_list)
datasets_tibble %>% 
  select(Package,Item, Title)

```

### Step 4 - use custom functions to get the R documentation for the data from within the package

```{r custom functions}
get_data_help<-function(dat,packname){
  dat=as.character(dat)
  packname=as.character(packname)
  find.package(packname)
  helptxt<-capture.output(tools::Rd2txt(utils:::.getHelpFile(utils::help(dat,paste0(packname))),options = list(sectionIndent = 0)))
return(helptxt)  
}

get_description_data<-function(helptxt){
  first<-which(grepl("n:",helptxt)==TRUE)
  last<-which(grepl("U_",helptxt)==TRUE)
  
  helptxt[first:last]
 }


```

```{r step 4}
helptxt<-get_data_help("EurasianLynx","AHMbook")
get_description_data(helptxt = helptxt)

```

